% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[sectioned]{dsyangres}
\usepackage[left =1in, top = 0.5in, bottom=0.5in]{geometry}

\usepackage{ifxetex}
\ifxetex
  \usepackage{fontspec}
  \setmainfont
  [ ExternalLocation ,
  Mapping = tex-text ,
  Numbers = OldStyle ,
  Ligatures = {Common,Contextual} ,
  BoldFont = texgyrepagella-bold.otf ,
  ItalicFont = texgyrepagella-italic.otf ,
  BoldItalicFont = texgyrepagella-bolditalic.otf ]
  {texgyrepagella-regular.otf}
  % Comment out the previous statement and uncomment the following
  % line to use the
  % Linux Libertine font (it has nice lignatures).
  % Make sure to have the `ttf-linux-libertine` package installed on
  % Ubuntu.
  % \setmainfont[Mapping=tex-text, Numbers=OldStyle,
  % Ligatures={Common,Contextual}]{Linux Libertine O}
\else
  \usepackage{tgpagella} % this case we lack lower case numbers,
  % ligatures and some typographic niceties
\fi

% the margin option causes section titles to appear to the left of body text
\textwidth=5.5in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\begin{document}

\name{ \hfil Daniel S. Yang \hfil % the \\[12pt] adds a blank line after name
}
\email{\hfil dsyang@andrew.cmu.edu }
\citizen{ \hfil(US Citizen)\hfil }
\phone{ \hfil Tel: 734-408-1407\hfil }

\address{{\bf School Address} \\
  5032 Forbes Ave. SMC 4932 \\ Pittsburgh, PA 15289  \\
         }
\address{{\bf Home Address} \\
  5313 Betheny Circle \\
  Superior Township, MI 48198 \\
   }


\begin{resume}

%%\section{Objective} Work on interesting problems with amazing people.


\section{Education}

\textbf{Carnegie Mellon University, Pittsburgh PA}
  \begin{itemize}
    \item Bachelors in Computer Science with a Robotics Minor \hfill \textbf{ Spring 2014}
      \\ QPA: 3.65/4.0
  \end{itemize}
% \textbf{Related Coursework:} \\
% 15-411 Compiler Design, 15-381 Artificial
% Intelligence, \\
% 16-311 Intro to Robotics, 15-312 Foundations of Programming
% languages,\\
% 15-237 Cross-Platform Mobile Web Apps

%\vspace{-1pt}
%\textbf{Huron High School, Ann Arbor MI}
%  \begin{itemize}
%    \item High School Diploma, GPA: 4.0/4.0 \hfill \textbf{ Spring 2010}
%  \end{itemize}


\section{Experience}

\textbf{Facebook}: Software Engineering Intern,
Menlo Park, CA \hfill \textbf{Summer 2013}
  \begin{itemize} \itemsep -2pt
    \item Worked on the site performance team writing internal \\
      tools to detect regressions and improve efficiency.
  \end{itemize}

\textbf{15-150 Principles of Functional
 Programming}: Teaching Assistant \hfill \textbf{Fall 2011 - Fall 2012}
 \begin{itemize} \itemsep -2pt
   \item Leading rest of course staff to create, modify, and\\
     grade hw/labs/tests for a 250+ student course taught in SML
 \end{itemize}

\textbf{Twilio Inc}: Software Engineering Intern,
 San Francisco, CA \hfill \textbf{Summer 2012}
  \begin{itemize} \itemsep -2pt
    \item Worked on the API team to improve robustness, readability, \\
      and metrics collection of the python codebase
    \item Contributed to the open source twilio-python helper library
  \end{itemize}

\textbf{SRT Solutions}: Software Developer Intern,
  Ann Arbor, MI \hfill \textbf{Summer 2011}
  \begin{itemize} \itemsep -2pt
    \item Developed fully-functioning Django web application for\\
      managing scholarships
%    \item Wrote back-end services for flex web app in ruby
%      on rails
    \item Practiced Behavior Driven Development with rspec
  \end{itemize}

%\textbf{Web App Team Lead Programmer, }
%  Huron BPA \hfill \textbf{Fall 2009, 2010}
%  \begin{itemize} \itemsep -2pt %reduce space between items
%    \item Developed various real-world web applications based on\\
%      topics provided by the Business Professionals of America \\
%      Workplace Skill Assessment Program.
%    \item Led team to place $2^{nd}$ in 2 state competitions
%  \end{itemize}


\section{Projects}

\textbf{Gcal Everywhere}
\hfill \textbf{Spring 2013}
  \begin{itemize} \itemsep -2pt
    \item A chrome extension that allows one to quickly add events to \\
      google calendar
    \item Publicly available on the chrome web store with over 150 users.
  \end{itemize}

\textbf{Hamilton} (http://hamilton.herokuapp.com)
\hfill \textbf{Spring 2013}
  \begin{itemize} \itemsep -2pt
    \item An simple interactive app for manipulation node-edge graphs.
    \item A Top-20 project at the Spring 2013 PennApps Hackathon.
    \item Pure javascript canvas app with a MongoDB/Python backend.
  \end{itemize}

\textbf{Tau} (https://github.com/srir/tau)
\hfill \textbf{Summer 2012}
  \begin{itemize} \itemsep -2pt
    \item A clean code-commenting/feedback site for academic use.
    \item A Top-10 project at the 2012 GreylockU Hackathon.
    \item Written in Node.js with MongoDB and Backbone.js.
  \end{itemize}

 \textbf{Rodney} (https://github.com/dsyang/rodney)
 \hfill \textbf{Spring 2012}
   \begin{itemize} \itemsep -2pt
     \item Your personal facebook chat secretary. Written in Python.
     \item Uses APIs from facebook, google, and twilio.
     \item Won the Facebook and Google awards at the 2012 Tartanhacks.
   \end{itemize}

% \textbf{pyKaruga} (https://github.com/dsyang/pyKaruga) \hfill \textbf{Spring 2011}
%   \begin{itemize} \itemsep -2pt
%     \item 2D multiplayer enabled space shooter game.
%     \item Written in python with pygame
%   \end{itemize}

%\textbf{Stever Assassins} (http://www.fulisoft.com/stassassins)
% \hfill \textbf{Fall 2010}
%  \begin{itemize} \itemsep -2pt
%    \item Web-based interface for ``assassins''
%    \item Written in PHP with Codeigniter
%  \end{itemize}
%  \vspace{-1pt}

\textbf{More projects} at http://github.com/dsyang

\section{Skills}

\begin{itemize} \itemsep -2pt
  \item Fluent in Mandarin Chinese
  \item Proficient with Standard ML, Haskell, Scala, Python, Ruby, PHP, C/C++
\end{itemize}

\section{Leadership \\ Activities}

\textbf{Campus Team Mamber} CMU Chak De Bhangra  \hfill \textbf{Present}

\textbf{Resident Assistant,} CMU Morewood E Tower \hfill \textbf{2011-2012}
  \begin{itemize} \itemsep -2pt
    \item In charge of helping 40 freshmen students have the\\ best
      first year college experience as possible
  \end{itemize}

% \textbf{Recording Engineer,} CMU College of Fine Arts \hfill
% \textbf{ Spring 2011}
%   \begin{itemize} \itemsep -2pt
%     \item Setup and record student concerts and recitals (audio/video)
%   \end{itemize}

\end{resume}
\end{document}
